Project Review

### 2025-05-03 review-Crammer/Cramer-project-review.qmd
# appropriately placing crammer's review

---
title: Project Review Template 
author: Mohammed Zuber
date: 4/23/2025
format: 
  html:
    toc: true
    toc-depth: 3
    number-sections: true
---

@@

Name of project reviewer: Mohammed Zuber

# Score 
Overall Score: 3 (Sufficient). 
The project is complete, detailed, and well-documented. It includes a comprehensive analysis using both statistical and machine learning approaches, with thorough explanation and reproducibility. Minor improvements are suggested, but they do not detract from the overall high quality of the work.

# Instructions
## Background, Context and Motivation
How well is the context of the project described? Is a comprehensive background, including summary of previous/related work given? Is the project well placed into the context of existing work (including proper referencing of existing work). Is it clear why the project was undertaken and what new information it hopes to provide?

@@

The background provides a clear rationale for studying health expenditure with references to prior studies. The objective to understand determinants such as GDP growth, corruption, and demographic variables is clearly articulated. However, a more detailed summary of the gaps in previous research and how this study addresses them would strengthen the motivation.

### Summary assessment 
* strong contextualization and motivation

@@

### Feedback and Comments
The research questions are explicitly stated and directly linked to the outcome variable (health expenditure per capita). The two-part objective — assessing key factors and their magnitude of influence — is well aligned with the analytical plan.

### Summary assessment
* question/hypotheses fully clear

@@

### Feedback and Comments
The data source (World Bank via OECD) is clearly identified, and the use of 462 observations from 38 countries is explained well. The GitHub repository is mentioned as the location for preprocessing steps, which is helpful. However, a codebook or variable dictionary is missing from the project folder, which makes it harder to understand the meaning and units of the 60+ variables used. Including even a brief data dictionary or a summary table with variable names and definitions would enhance transparency and usability.

### Summary assessment
* source and overall structure of data somewhat explained

@@

### Feedback and Comments
Exploratory analysis is well-executed with appropriate figures (e.g., trends, correlation plots) and justified variable selection. The well documented comments on how much time the code takes to run is commendable.

### Summary assessment
* essentially no weaknesses in wrangling and exploratory component

@@

The OLS regression is appropriate and well-justified for panel data. The inclusion of cross-validation and RF as robustness checks adds value.

### Summary assessment
* strong and reasonable analysis

@@

### Feedback and Comments
Figures and tables are informative and generally clear. However, a few visuals could benefit from better axis labeling and reduced clutter. The narrative does a good job walking the reader through the findings.

### Summary assessment
* results are very well presented

@@

The discussion effectively synthesizes the key findings and connects them to existing literature, reinforcing the credibility of the results. The implications for public policy and international resource allocation are thoughtfully addressed. However, the discussion lacks a clear summary of the study’s strengths and limitations. For instance, a major strength is the comprehensive modeling approach, including OLS and Random Forest with validation across datasets. A notable limitation is the potential overfitting in the RF model and the absence of detail on how missing data and variable collinearity were handled. Including these would provide a more balanced and critical reflection on the results.

### Summary assessment
* minor parts wrong, missing or unclear

## Further comments
none

@@

The project folder is clearly organized, with appropriately named files and a logical directory structure. There are no unnecessary or junk files, and the layout makes it easy to follow the workflow from raw data to final analysis and figures. The repository reflects good practices in reproducible research and is easy to navigate.

### Summary assessment
* well structured

@@

The project is well documented, with clear and consistent comments throughout the code. Each line of code is annotated to explain its purpose, making the analysis easy to follow. The Rmd files guide the reader through the workflow step by step, and the folder structure further supports understanding. Overall, the documentation reflects thoughtful effort to ensure transparency and reproducibility.

### Summary assessment
* fully and well documented

@@

The project is fully reproducible, with all code executing smoothly and generating the expected outputs, including figures and tables. The analysis runs without any need for manual intervention, and all necessary data files and scripts are included in the repository. This reflects strong adherence to reproducible research standards.

### Summary assessment
* fully reproducible without issues

@@

The project demonstrates a strong level of thoroughness. Multiple modeling approaches were considered — including OLS and Random Forest — and each was tested using cross-validation and out-of-sample performance.

### Summary assessment
* strong level of thorougness

@@

Overall, Great Job!

>>>>

---
title: Project Review
author: Annalise Cramer
date: 4/25/25
format: 
  html:
    toc: true
    toc-depth: 3
    number-sections: true
---

@@

Name of project reviewer: Annalise Cramer

## Background, Context and Motivation
How well is the context of the project described? Is a comprehensive background, including summary of previous/related work given? Is the project well placed into the context of existing work (including proper referencing of existing work). Is it clear why the project was undertaken and what new information it hopes to provide?

@@

I think defined OECD starting in the abstract would be helpful. More background information on the problem would be helpful-- why do we care about health expenditure? Why look at different countries? As someone who doesn't know much about this field, I would guess this has something to do with different healthcare systems in various countires and is this some sort of measure of efficency of the different systems? Idk, but add some more to fill it out.

### Summary assessment (PICK ONE, DELETE THE OTHERS)

Some contextualization and motivation

@@

I liked the part about how this research could inform policy.

### Summary assessment

Question/hypotheses fully clear

@@

Data source is well explained and 38 countries is described. What years does this data cover, and what types of variables are in this dataset?

Edit: I see there's more information on the data that answers some of my questions. I think combining this information into one place would be helpful.

### Summary assessment

Source and overall structure of data somewhat explained

@@

This is some of the best documented code I've seen all semester. I was easily able to follow along with data manipulation and what the figures were for, and the figures looked excellent. I got an error at line 435 for france_data, maybe you had a line in there ealier that got removed? As I continue, correlation plots look great. You provided plenty of description in your manuscript for EDA.

### Summary assessment

Essentially no weaknesses in wrangling and exploratory component

@@

I'm able to follow the analysis successfully. First, you group the variables into theme categories. I'm used to seeing forwards or backawards selection for model building, so I'm a lttle unfamiliar with this method-- could you explain more? The regression ran smoothly.

For 5.2.3 in your manuscript where you type the regression equation, at line 163 in your manuscript, the equation needs some reformatting. Maybe make the vairable names abgreviated subscripts?

Adding in a little bit more motivation for exploring the random forest model would help

You can save yourself some time but just loading library(tidyverse), which includes: ggplot2, dplyr, tidyr, readr, purrr, tibble, stringr, and forcats, and some others too. It's a little easier than typing a bunch of those out :)

### Summary assessment

Strong and reasonable analysis

@@

10/10 figures and tables

### Summary assessment

Results are very well presented

@@

Good explanation and interpretation of results and their implications. Could use discussion of limitations.

### Summary assessment

Minor parts wrong, missing or unclear

@@

I was able to find everything with no issues. Copy/pasting the codebook into some of the EDA code could be helpful.

### Summary assessment

Well structured

@@

Excellent no notes

### Summary assessment

Fully and well documented

@@

I was able to run everything with no issues

### Summary assessment

Fully reproducible without issues

@@

There was lots of exploration on which vairables to include in the model, and ML altetnatives were epxlored.

### Summary assessment

Strong level of thorougness

@@

Overall you're in really good shape. Filling it out a little more in some parts will make it even better.
